DRAFT

### 2022-11-03 Draft.Rmd
Update Draft.Rmd

### • Weekend and holiday
```{r echo=FALSE}
kable(count(df2, weekend)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```
```{r echo=FALSE}
kable(count(df2, holiday)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

## 1.3 Findings
### • Mean prices for countries

```{r echo=FALSE}
datasummary(trueprice*country ~ Mean + Max + Min, data=df2)%>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

>>>>

### • Weekend and holiday
### 36193 records were made on weekends (66%),  and 18754 - on weekdays (34%)

```{r echo=FALSE}
kable(count(df2, weekend)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

### Only 21% (11728) of all observations were made on holidays.

```{r echo=FALSE}
kable(count(df2, holiday)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

## 1.3 Findings. 
### For this project, we wanted to find the best deal among different types of accommodation in Central European countries. 
### Consequently, we formulated the question: 
* *How does the average price change for different values of explanatory variables?*

### • Mean prices for countries

```{r}
datasummary(trueprice*country ~ Mean + Max + Min, data=df2)%>%
  kableExtra::kable_styling(latex_options = "hold_position")
```
